\newpage

 \vspace*{1in}

 \emph{Dedicated to my mother, Meishen and my father, Kunlong}

\newpage
\chapter*{Acknowledgements}
  First of all, I would like to thank my advisor Prof. Donal Day for his great support and guidance. He brought me into his group to work on this exciting field. He was always available when I needed his help, standing out for me every time when I was in trouble, encouraging  me to seek more challenges and develop my own academic career. I was also very fortunate to join the E08-014 collaboration and closely work with three other spokespeople: John Arrington, Doug Higinbotham and Patricia Solvignon-Slifer. I have learned a lot from John, not only the knowledge in nuclear physics but also the techniques of analysis and problem-solving skills. Doug is always very supportive, and with his trust and encouragement, I have earned many opportunities to improve my abilities, which greatly boosted my confidence and made me become more versatile in physics. Patricia used her experience to help me not only on the detailed research work, but also on how to become a successful graduate student and how to build rapport with other colleagues. She pointed out my mistakes in the most comfortable way and cared about me and my families. I also received many help from other people in this collaboration, especially Nadia Fomin, who gave me a lot of help on the data analysis. I always feel lucky and grateful that I can own such a supportive team in my career.
  
  Thank to my colleagues and friends in the E08-014 collaboration and other four collaborations in the SRC family during run period of the spring 2011. I'd like to mention these hard working graduate students: David Anez, Navaphon Muangma and Lawrence Selvy; and also our post-docs: Aidan Keller, Charles Hanretty and Vince Sulkosky. Your big contributions were the main reason that our experiments had been so successful. I would like to thank Alexander Camsonne, Jian-Ping Chen, Javier Gomez, Ole Hanson, John LeRose, Bob Michel, Bogdan Wojtsekhowski and all other Hall-A staffs for supporting our experiments. I want to specially thank Vince and Alexandria who patiently taught me the knowledge of the Hall-A detectors and electronics, worked side-by-side with me to prepare the online data checkout and continued to offer guidance on my offline data analysis. Thank Ed. Folts, Jack Segal and all other Hall-A technicians for installing and maintaining the instruments. I would like to thank Dave Meekins and the target group on the support of our target system. I also want to mention the hard working of the staffs in the accelerator division. I am grateful for those colleagues who acted as run coordinators, filled our shifts, monitored the data quality and completed our run plans.
   
   I would like to thank my advisor at Hampton University, Dr. Liguang Tang, who brought me into the field of experimental nuclear physics and guided me to work on the Hypernuclear program in Hall-C. I won't forget our post-doc, Lulin Yuan who showed great patience in teaching me the knowledge of data analysis and earnestly answered every question. He set up a good example of how to work with beginners. I also want to thank Chunhua Chen for working so hard with me to prepare the HES experiment. I am grateful to colleagues in the Hypernuclear collaboration: Prof. Jorg Reinhard, Prof. Nakamura and Prof. Hashimoto, and all other graduate students and post-docs. I especially want to mention Prof. Hashimoto, who played the leading role in the Hypernuclear physics. I still remembered that when he heard I decided to leave the collaboration, he had a long conversation with me and encouraged me to make the best choice for the good of my academic career. He passed away in 2011 before I had a chance to visit his family but I will never forget him, a respectful scientist and a gentleman.

   I am grateful to Prof. Blaine Norum and Prof. Liyanaga who accepted me to continue studying at UVa. I also want to thank these lovely ladies in the office of our department: Dawn, Tammie, Helen, Beth and so on. 
   
   I also want to thank Prof. Bitao Hu, the thesis advisor of my Bachelor degree at Lanzhou University and also a very good friend. He shared his experience and knowledge with me, introduced to me the JLab physics, encouraged and helped me to apply for a Ph.D program in US. My life would have been in a completely different track if I did not meet him in the college.
   
   I would like to thank Chunhua Chen, Xin Qian, Yi Qiang, Huan Yao, Xiaohui Zhan and others, who have been my good friends for many years and take care of each other. Thank Lulin Yuan and Xiaoyan Lin, Xiaofeng Zhu and Change Ma, Bo Zhan and Yangping Yang, for taking care of me when I just came to US and helping me to fit in here. I also want to thank all other friends living in Newport News and Charlottesville. Your friendship is very important to me.
   
   My families are always the most important part of my life, although I haven't spent too much time with them these years. My parents did a great job in raising me, despite the fact that they have sacrificed a lot. For years they had to live a hard life to support my education. Instead of forcing me to choose other careers that I can make more money to support the family, they encourage me to pursue and persist my dream. Although I have been trying to make them proud, I would never be able to repay their selflessness.
   
   Finally, thank you, my dear wife, Zongwen Yang, for all the wonderful moments we have been sharing together. You take care of me and our families without any complains. You tolerate my bad temper and strong character. I feel so lucky to have you in my live and without you, I would have been a completely different person and live a different and difficult life. Thank you for loving me, putting up with me and helping me to write this thesis. 